Quality assurance of digital twins -- An experience report in the automotive industry

### 2023-02-28 manuscripts/paper-1/main.tex
Literature Research is revised

%%\documentclass[9pt,conference]{IEEEtran}
\documentclass{llncs}
\usepackage[colorlinks,allcolors=blue]{hyperref}
\usepackage[T1]{fontenc}
\usepackage{listings}
\usepackage{graphicx}
\usepackage{amsfonts}
\usepackage{verbatim}

@@

    The notion of the digital twin, which has gained popularity in 
    recent years, is often subject to vague and ambiguous envisions\cite{Review1}.
    The mispresenting this notion began with the physical twin of the Apollo 13 spacecraft. 
    The twin of Apollo 13 was merely a tangible replication of the spacecraft that has been utilised in the physical simulations. 
    Even though the digital aspect was expected to be present, there wasn't\cite{GrievesApollo13}.
    Another physical twin is the historic D-day map (also known as the Big Board) in Southwick House England, 
    which was used simultaneously before and during operation, can be argued to be similar. 
    The board was a twin of the operation, and it included model of battalions and ships that reflected the actual 
    locations of the corresponding formations. Furthermore, synchronisation was 
    implemented to give directives from the real system to control the operation 
    flow and to update the physical twin state\cite{AMRC}.
    In contrast, a digital twin is a virtual counterpart of a real system, which should 
    be synchronized with a selected frequency and fidelity\cite{Review1}\cite{Review2}\cite{digitaltwinconsortium2022}.

@@

    %%//TODO MAYBE BETTER FORMATING HERE
    Digital twins are complex evolvable systems, that are not only adapting to the changes in the environment, 
    also are able to change their internal structure \cite{ZHANGUPDATEMETHOD}\cite{MobusSystemTheory}. 
    To making sure that these complex evolvable systems can provide a certain quality is a mere challange whom wants to construct a digital twin.

@@

    \subsection{Research objective}
    Find an approach to assess the quality of Digital twins~\cite{Jones2020}

    \subsection{Research question}\label{section: Research Questions}
    What is the quality of digital twins?
    What is the state art of digital twin quality?

    \subsection{Research methodology}
    TODO

@@

    \subsection{Simulation Quality}
    Simulation models are not merely virtual systems; 
    they are also abstracted systems, which are nothing more than imitations or, 
    to be more precise, abstractions of real systems. 
    We are simulating something every day when we are trying 
    to predict the future outcome or abstractly thinking about the past state of some occurred event. 
    An important element to remember is that we mentally model the 
    event before executing the simulation. However, most of the simulation processes we see today, 
    are computer-based, with software programs. These programs 
    include ANSYS\cite{Ansys}, ABAQUS\cite{Abaqus}, and 
    AnyLogic\cite{AnyLogic}, as examples. Consequently, the idea of simulation software programs emerges.

    Validation and verification can be used to evaluate the quality characteristics of the simulation model \cite{StewartSimulation} \cite{VerificationValidationSergent} \cite{OsmanBalci}. 
    Validation is the process of evaluating the simulation quality of the model in comparison to the real system from the perspective of the model's intended applications. 
    On the other hand, verification is a procedure to evaluate a simulation model's implementation and its associated data concerning the conceptual description and specifications of the model developer.

@@

    \subsubsection*{Literature Search Methodology}
    Google Scholar (GS), Scopus (SCP) and Research Rabbit (RR) tools are used to fulfill our requirements for the literature review. Since there is a great number of digital twin publications in academics,
    narrowing the research is necessary, so the following algorithm with two levels of filtering will be applied.

    Initial filtering has been done with the following criteria
    \begin{itemize}
        \item  Dissertations should be written in English and published in a journal/conference.
        \item  Search term should be exactly searched
    \end{itemize}
    Filtering query calls for the GS and SCP are the following
    \begin{itemize}
        \item Google Scholar = `search term'
        \item Scopus = ALL (`digital twin quality') AND (LIMIT-TO (LANGUAGE, `English'))
    \end{itemize}
    After the initial filtration, the second filtering which is a manual investigation should occur with the following filtering criteria:
    \begin{itemize}
        \item  Remove Duplications
        \item  Remove the dissertations which are not English
        \item  Proper literature review should be present in the selected dissertation
        \item  Abstract and conclusion should be relevant to the search term
    \end{itemize}

@@

    \subsubsection*{Literature Result}
    The search term `digital twin quality' initially yielded 41 results on Google Scholar and three on Scopus. 
    After the second filtering stage, six duplicate dissertations were removed, along with ten dissertations that were not in English. As a result, only nine dissertations passed all the criteria and were inspected, while the remainder were rejected.

    The search term `digital twin verification' initially yielded, resulting in nineteen hits on Google Scholar and zero on Scopus. After the second filtering stage, one duplicate dissertation was removed, along with two dissertations that were not in English.
    As a result, all dissertations were rejected.

    The search term `digital twin validation' was filtered initially, resulting in fifty-nine hits on Google Scholar and zero on Scopus. After the second filtering stage, four duplicate dissertations were removed, along with 4 dissertations that were not in English.
    As a result, eight dissertations passed all the criteria and were inspected while the remainder were rejected.

    \subsubsection*{Findings}

    The findings are the following;
    \begin{itemize}
        \item Shcherba et al. center their attention on the model quality, which is an observation for a digital twin subsystem. Despite being a crucial component of the digital twin, models alone cannot be used to assess the quality of the digital twin~\cite{Shcherba}.
        \item A consistency evaluation approach for digital twin models was developed by He Zhang et al. and can be used to assess the quality of the models. Additionally, 
        the authors discuss crucial ideas like consistency between real and virtual systems and ultra-fidelity models. The improvement of the service component is the primary emphasis of this article. Tao's five-dimensional digital twin concept includes this component~\cite{ZHANGEVALUATIONMETHOD}.
        \item He Zhang et al. introduces the updating method for digital twin models in yet another insightful article. Once more, the accuracy and coherence of the model concepts were addressed~\cite{ZHANGUPDATEMETHOD}.
        \item Selch et al. work is the only one that discusses the quality of the digital twin. The paper presents a machine-learning approach based on Bayesian networks to track the quality of the digital twin. The unique aspect of this study is that the author, rather than just analyzing the digital twin as a single system, determines the contributions of subsystems to forecast the overall quality of the digital twin. The digital couplings, which are linkages between the subsystems, are also mentioned by Selch et al. as a source of extra uncertainty. 
        Since only one digital twin has been used in practice, multiple subsystem digital twins have not been validated~\cite{QualityMonitoringofCoupledDigitalTwins}.
        \item The stability of the digital twin models was assessed using the Kolmogorov-Smirnov statistical test, which measures the degree of similarity between the probability distribution of the model's predictions and the distribution of the actual data~\cite{RadarDigitalTwin}.
        \item Edward Y. Hua et al. identify five open problems with digital twin model validation, including modeling realism, data uncertainty, system dynamics, use-case alignment, and reporting invalid modes. To address these challenges, the authors propose a digital-twin model validation framework. Additionally, the paper highlights three areas for future research, 
        including uncertainty and sensitivity analysis, model validation of system-of-systems, and combining expert knowledge and collected data~\cite{ValidationofDigitalTwins}.
        \item Shotaro Hamato et al. demonstrated real-time anomaly detection was successfully demonstrated using the Unscented Kalman Filter with the digital twin model, but determining the appropriate threshold for anomaly detection remains an issue~\cite{JapeneseKalmanFilterCorrectness}.
    \end{itemize}

>>>>

%%\documentclass[9pt,conference]{IEEEtran}
\documentclass{llncs}
\usepackage[colorlinks,allcolors=blue]{hyperref}
\usepackage[T1]{fontenc}
\usepackage{listings}
\usepackage{graphicx}
\usepackage{amsfonts}
\usepackage{verbatim}
\usepackage{cite}

@@

    The notion of the digital twin, which has gained popularity in 
    recent years, is often subject to vague and ambiguous envisions\cite{Review1}.
    The mispresenting this notion began with the physical twin of the Apollo 13 spacecraft. 
    The twin of Apollo 13 was merely a tangible replication of the spacecraft that has been utilised in the physical simulations. 
    Even though the digital aspect was expected to be present, there wasn't\cite{GrievesApollo13}.
    Another physical twin is the historic D-day map (also known as the Big Board) in Southwick House England, 
    which was used simultaneously before and during operation, can be argued to be similar. 
    The board was a twin of the operation, and it included model of battalions and ships that reflected the actual 
    locations of the corresponding formations. Furthermore, synchronisation was 
    implemented to give directives from the real system to control the operation 
    flow and to update the physical twin state\cite{AMRC}.
    In contrast, a digital twin is a virtual counterpart of a real system, which should 
    be synchronized with a selected frequency and fidelity\cite{Review1,Review2,digitaltwinconsortium2022}.

@@

    Digital twins are highly intricate and adaptable systems that possess the capability to not only respond to environmental 
    changes but also modify their internal structure \cite{ZHANGUPDATEMETHOD,MobusSystemTheory}. Therefore, ascertaining a 
    requisite level of quality for the construction of a digital twin is an arduous undertaking.

@@

    %%
    %%\subsection{Research objective}
    %%Find an approach to assess the quality of Digital twins~\cite{Jones2020}

    %%\subsection{Research question}\label{section: Research Questions}
    %%What is the quality of digital twins?
    %%What is the state art of digital twin quality?

    %%\subsection{Research methodology}
    %%TODO

@@

    \subsection{Simulation Quality}
    Simulation models are not merely virtual systems; they are also abstracted systems, 
    which are nothing more than imitations or, to be more precise, abstractions of the real systems. 
    In fact, everyday, simulation of the real systems occurs in the human brain when prediction of the future outcome or  about the 
    past state of some occured event required\cite{MobusSystemTheory}. However, most of the simulation processeses are computer 
    based with software programs. Consequently, the idea of simulation software programs emerges. 
    For example, ANSYS\cite{Ansys}, ABAQUS\cite{Abaqus}, and AnyLogic\cite{AnyLogic} are examples of these simulation software programs.

    Validation and verification is used to evaluate the quality characteristics of the simulation 
    model \cite{StewartSimulation,VerificationValidationSergent,OsmanBalci}. 
    Validation is the process of evaluating the simulation quality of the model in comparison to 
    the real system from the perspective of the model's intended applications.
    On the other hand, verification is a procedure to 
    evaluate a simulation model's implementation and its associated 
    data concerning the conceptual description and specifications of the 
    model developer\cite{StewartSimulation,VerificationValidationSergent}.

@@

    \subsubsection*{Literature Search Methodology}
    To conduct a thorough literature review on digital twin publications, tools such as Google Scholar and Scopus are utilized. Due to the vast amount of available literature, it is necessary to narrow down the scope of the research. 
    Therefore, a multi-level filtering algorithm is employed to refine the search results.

    The first level of filtering for the literature review on digital twin publications involves specific criteria. These include that dissertations must be written in English and 
    published in a journal or conference, and that the search term must be an exact match. To execute this initial filtration, 
    the following queries are used for Google Scholar and Scopus respectively: "search term" and ALL ("digital twin quality") AND (LIMIT-TO (LANGUAGE, "English")).

    After the initial filtering, a second level of manual investigation is necessary. The following criteria are used for this level of filtering:    
    \begin{itemize}
        \item  Eliminating duplicates
        \item  Removing dissertations that are not in English
        \item  Ensuring that selected dissertations have a proper literature review
        \item  Ensuring that abstract and conclusion are relevant to the search term
    \end{itemize}

@@

    \subsubsection*{Literature Search Result}
    The search for "digital twin quality" initially resulted in 41 hits on Google Scholar and 3 on Scopus. 
    After the second level of filtering, 6 duplicate dissertations were removed and 10 dissertations that were not in English were also eliminated. 
    This left only 9 dissertations that met all the criteria and were reviewed.

    The search for "digital twin verification" initially resulted in 19 hits on Google Scholar and none on Scopus. 
    After the second level of filtering, one duplicate dissertation was removed and two dissertations that were not in 
    English were also eliminated. As a result, all dissertations were rejected.

    The search for "digital twin validation" initially resulted in 59 hits on Google Scholar and none on Scopus. 
    After the second level of filtering, 4 duplicate dissertations were removed and 4 
    dissertations that were not in English were also eliminated. This left only 8 dissertations that met all the criteria and were reviewed.

    After a thorough review of 17 research papers, a number of significant findings were revealed.

    First, it was noted that Shcherba et al.  focus on the importance of model quality as an observation for a digital twin subsystem. 
    However, they acknowledged that the quality assessment of the digital twin cannot solely rely on models~\cite{Shcherba}.

    He Zhang et al.  developed a consistency evaluation approach for digital twin models, which can be used to assess their quality. 
    The authors also discuss essential concepts, such as consistency between real and virtual systems and ultra-fidelity models. 
    This article emphasizes the improvement of the service component of the digital twin~\cite{ZHANGEVALUATIONMETHOD}.

    He Zhang et al. introduced the updating method for digital twin models in yet another insightful article.
    Once more, the accuracy and coherence of the model concepts were addressed~\cite{ZHANGUPDATEMETHOD}.

    Selch et al.  present a machine-learning approach based on Bayesian networks to track the quality of the digital twin. 
    The unique aspect of this study is that the authors determine the contributions of subsystems to forecast the overall quality of the digital twin, 
    rather than just analyzing it as a single system. The digital couplings, which are linkages between the subsystems, are also identified as a source of extra uncertainty. 
    However, since only one digital twin has been used in practice, multiple subsystem digital twins have not been validated~\cite{QualityMonitoringofCoupledDigitalTwins}.

    Additionally, the stability of digital twin models was assessed by another study using the Kolmogorov-Smirnov statistical test, 
    which measures the degree of similarity between the probability distribution of the model's predictions and the distribution of the actual data~\cite{RadarDigitalTwin}.

    Edward Y. Hua et al. identify five open problems with digital twin model validation, including modeling realism, data uncertainty, system dynamics, use-case alignment, and reporting invalid modes. To address these challenges, the authors propose a digital-twin model validation framework. The paper also highlights three areas for future research, 
    including uncertainty and sensitivity analysis, model validation of system-of-systems, and combining expert knowledge and collected data ~\cite{ValidationofDigitalTwins}.

    Finally, Shotaro Hamato et al.  demonstrated successful real-time anomaly detection using the Unscented Kalman Filter with the digital twin model. 
    However, determining the appropriate threshold for anomaly detection remains an issue~\cite{JapeneseKalmanFilterCorrectness}.

    Overall, these studies provide valuable insights into various aspects of digital twin quality assessment, 
    including model consistency, stability, and validation, as well as machine learning-based approaches and real-time anomaly detection. 
    However, the identified open problems, including modeling realism, data uncertainty, system dynamics, use-case alignment, and reporting invalid modes, 
    call for further research in the field to improve the quality and reliability of digital twins. Moreover, 
    the lack of well-defined quality parameters for digital twins poses a significant challenge in ensuring their quality,
    which necessitates the development of appropriate quality metrics and standards for digital twins.
